\section{Courses and Meetings Attendance}

\cvitem{2019}{\emph{ASHG}, Houston -- US.}
\cvitem{2019}{\emph{BioC}, Rockefeller University, New York -- US.}
\cvitem{2019}{\emph{BoG}, Cold Spring Harbor -- US.}
\cvitem{2019}{\emph{RStudio conf}, Austin -- US.}
\cvitem{2019}{\emph{Pacific Symposium on Biocomputing (PSB)}, Hawaii -- US.}
\cvitem{2018}{\emph{Biological Data Science (biodata18)}, Cold Spring Harbor -- US.}
\cvitem{2018}{\emph{ASHG}, San Diego -- US.}
\cvitem{2018}{\emph{SAGES}, Philadelphia -- US.}
\cvitem{2018}{\emph{SOBP}, New York -- US.}
\cvitem{2018}{\emph{BoG}, Cold Spring Harbor -- US.}
\cvitem{2018}{\emph{rOpenSci unconf}, Seattle -- US.}
\cvitem{2017}{\emph{JSM}, Baltimore -- US.}
\cvitem{2017}{\emph{BioC}, Dana-Farber Cancer Institute, Boston -- US.}
\cvitem{2017}{\emph{ICSA}, Chicago -- US.}
\cvitem{2017}{\emph{SOBP}, San Diego -- US.}
\cvitem{2016}{\emph{SACNAS}, Long Beach -- US.}
\cvitem{2016}{\emph{ENAR}, Austin -- US.}
\cvitem{2015}{\emph{ENAR}, Miami -- US.}
\cvitem{2014}{\emph{is3b}, INMEGEN, Mexico City -- MX.}
\cvitem{2014}{\emph{BioC}, Dana-Farber Cancer Institute, Boston -- US.}
\cvitem{2014}{\emph{IDIES2014}, Johns Hopkins University, Baltimore -- US.}
\cvitem{2014}{\emph{ENAR}, Baltimore -- US.}
\cvitem{2014}{\emph{Delta Omega Poster Competition}, Johns Hopkins University, Baltimore -- US.}
\cvitem{2014}{LCG 10 year anniversary, LCG-UNAM, Cuernavaca -- MX.}
\cvitem{2013}{\emph{Genomics and Bioinformatics Symposium}, Johns Hopkins University, Baltimore -- US.}
\cvitem{2013}{\emph{useR2013}, Albacete -- Spain.}
\cvitem{2011}{\emph{BioC}, FHCRC, Seattle -- US.}
\cvitem{2010}{\emph{From Functional Genomics to Systems Biology}, EMBL, Heidelberg -- Germany.}
\cvitem{2010}{\emph{BioC}, FHCRC, Seattle -- US.}
\cvitem{2009}{\emph{BioC}, FHCRC, Seattle -- US.}
\cvitem{2009}{Course on Oral Communication taught by the master Rafael Popoca, CCG-UNAM, Cuernavaca -- MX.}
\cvitem{2008}{\emph{BioC}, FHCRC, Seattle -- US.}
\cvitem{2008}{\emph{A Short R/Bioconductor Course} by James Bullard from UC Berkeley, LCG-UNAM, Cuernavaca -- MX.}
\cvitem{2007}{\emph{Boston Bacterial Meeting}, Boston -- US.}
\cvitem{2007}{\emph{Retreat of the Department of Microbiology and Molecular Genetics - Harvard}, Boston -- US.}
\cvitem{2006}{\emph{Winter School in Genomics}, CCG-UNAM, Cuernavaca -- MX.}
\cvitem{2005}{\emph{HUGO 2005}, Kyoto -- Japan.}
