\section{Publications}

$*$ indicates equal contribution, $\dagger$ indicates corresponding author

\subsection{Pre-prints}
    \begin{enumerate}
        \item Eddie-Luidy Imada$^{*}$, Diego Fernando Sanchez$^{*}$, \textbf{Leonardo Collado-Torres}, Christopher Wilks, Tejasvi Matam, Wikum Dinalankara, Aleksey Stupnikov, Francisco Lobo-Pereira, Chi-Wai Yip, Kayoko Yasuzawa, Naoto Kondo, Masayoshi Itoh, Harukazu Suzuki, Takeya Kasukawa, Chung-Chau Hon, Michiel JL de Hoon, Jay W Shin, Piero Carninci, FANTOM consortium, Andrew E Jaffe, Jeffrey T Leek, Alexander Favorov, Gloria R Franco, Ben Langmead$\dagger$, Luigi Marchionni$\dagger$. Recounting the FANTOM Cage Associated Transcriptome. \emph{bioRxiv} 659490 (2019). doi: \httplink[10.1101/659490]{doi.org/10.1101/659490}.
        
        \item Ashkaun Razmara, Shannon E Ellis, Dustin J Sokolowski, Sean Davis, Michael D Wilson, Jeffrey T Leek, Andrew E Jaffe, \textbf{Leonardo Collado-Torres}$\dagger$. \emph{recount-brain}: a curated repository of human brain RNA-seq datasets metadata. \emph{bioRxiv} 618025 (2019). doi: \httplink[10.1101/618025]{doi.org/10.1101/618025}.
        
        \item Sebastian Guelfi$^{*}$, Karishma D’Sa$^{*}$, Juan Botía$^{*}$, Jana Vandrovcova, Regina H. Reynolds, David Zhang, Daniah Trabzuni, \textbf{Leonardo Collado-Torres}, Andrew Thomason, Pedro Quijada Leyton, Sarah A. Gagliano, Mike A. Nalls, UK Brain Expression Consortium, Kerrin S. Small, Colin Smith, Adaikalavan Ramasamy, John Hardy, Michael E. Weale$\dagger$, Mina Ryten$\dagger$. Regulatory sites for known and novel splicing in human basal ganglia are enriched for disease-relevant information. \emph{bioRxiv} 591156 (2019). doi: \httplink[10.1101/591156]{doi.org/10.1101/591156}.
        
        \item David Zhang$^{*}$, Sebastian Guelfi$^{*}$, Sonia Garcia Ruiz, Beatrice Costa, Regina H Reynolds, Karishma D'Sa, Wenfei Liu, Thomas Courtin, Amy Peterson, Andrew E Jaffe, John Hardy, Juan Botia, \textbf{Leonardo Collado-Torres}, Mina Ryten. Incomplete annotation of OMIM genes is likely to be limiting the diagnostic yield of genetic testing, particularly for neurogenetic disorders. \emph{bioRxiv} 499103 (2018). doi: \httplink[10.1101/499103]{doi.org/10.1101/499103}.
        
        \item Amanda J. Price$^{*}$, \textbf{Leonardo Collado-Torres}$^{*}$, Nikolay A. Ivanov, Wei Xia, Emily E. Burke, Joo Heon Shin, Ran Tao, Liang Ma, Yankai Jia, Thomas M. Hyde, Joel E. Kleinman, Daniel R. Weinberger, Andrew E Jaffe. Divergent neuronal DNA methylation patterns across human cortical development: Critical periods and a unique role of CpH methylation. \emph{bioRxiv} 428391 (2018). doi: \httplink[10.1101/428391]{doi.org/10.1101/428391}.
        
        \item Emily E Burke$^{*}$, Joshua G Chenoweth$^{*}$, Joo Heon Shin, \textbf{Leonardo Collado-Torres}, Suel Kee Kim, Nicola Micali, Yanhong Wang, Richard E Straub, Daniel J Hoeppner, Huei-Ying Chen, Alana Lescure, Kamel Shibbani, Gregory R Hamersky, BaDoi N Phan, William S Ulrich, Cristian Valencia, Amritha Jaishankar, Amanda J Price, Anandita Rajpurohit, Stephen A Semick, Roland Bürli, James C Barrow, Daniel J Hiler, Stephanie Cerceo Page, Keri Martinowich, Thomas M Hyde, Joel E Kleinman, Karen F Berman, José A Apud, Alan J Cross, Nick J Brandon, Daniel R Weinberger, Brady J Maher, Ronald DG McKay$\dagger$, Andrew E Jaffe$\dagger$. Dissecting transcriptomic signatures of neuronal differentiation and maturation using iPSCs. \emph{bioRxiv} 380758 (2018). doi: \httplink[10.1101/380758]{doi.org/10.1101/380758}.
        
        \item Fu J, Kammers K, Nellore A, \textbf{Collado-Torres L}, Leek JT, Taub MA. RNA-seq transcript quantification from reduced-representation data in recount2. \emph{bioRxiv} 247346 (2018). doi: \httplink[10.1101/247346]{doi.org/10.1101/1247346}.
    \end{enumerate}

\subsection{Peer-reviewed}
    \begin{enumerate}
        \item \textbf{Leonardo Collado-Torres}, Emily E Burke, Amy Peterson, JooHeon Shin, Richard E Straub, Anandita Rajpurohit, Stephen A Semick, William S Ulrich, BrainSeq Consortium, Amanda J Price, Cristian Valencia, Ran Tao, Amy Deep-Soboslay, Thomas M Hyde, Joel E Kleinman, Daniel R Weinberger$\dagger$, Andrew E Jaffe$\dagger$. Regional heterogeneity in gene expression, regulation, and coherence in the frontal cortex and hippocampus across development and schizophrenia. \emph{Neuron} 2019. doi: \httplink[10.1016/j.neuron.2019.05.013]{doi.org/10.1016/j.neuron.2019.05.013}
        \\ Pre-print: \emph{bioRxiv} 426213 (2018). doi: \httplink[10.1101/426213]{doi.org/10.1101/426213}.
        
        \item Carrie Wright$^{*}$, Anandita Rajpurohit$^{*}$, Emily E. Burke, Courtney Williams, \textbf{Leonardo Collado-Torres}, Martha Kimos, Nicholas J. Brandon, Alan J. Cross, Andrew E. Jaffe, Daniel R. Weinberger$\dagger$, Joo Heon Shin$\dagger$.Comprehensive assessment of multiple biases in small RNA sequencing reveals significant differences in the performance of widely used methods. \emph{BMC Genomics} (2019). doi: \httplink[10.1186/s12864-019-5870-3]{doi.org/10.1186/s12864-019-5870-3}.
        \\ Pre-print: \emph{bioRxiv} 445437 (2018). doi: \httplink[10.1101/445437]{doi.org/10.1101/445437}.
        
        \item Stephen A Semick, Rahul A Bharadwaj, \textbf{Leonardo Collado-Torres}, Ran Tao, Joo Heon Shin, Amy Deep-Soboslay, James R. Weiss, Daniel R Weinberger, Thomas M Hyde, Joel E Kleinman, Andrew E Jaffe$\dagger$, Venkata S Mattay$\dagger$. Integrated DNA methylation and gene expression profiling across multiple brain regions implicate novel genes in Alzheimer's disease. \emph{Acta Neuropathologica} 2019. doi: \httplink[10.1007/s00401-019-01966-5]{doi.org/10.1007/s00401-019-01966-5}
        \\ Pre-print: \emph{bioRxiv} 430603 (2018). doi: \httplink[10.1101/430603]{doi.org/10.1101/430603}.
            
        \item Helena Kuri-Magaña, \textbf{Leonardo Collado-Torres}, Andrew E Jaffe, Humberto Valdovinos-Torres, Marbella Ovilla-Muñoz, Juan M Téllez-Sosa, Laura C Bonifaz-Alfonzo, Jesús Martínez-Barnetche. Non-coding Class Switch Recombination-Related Transcription in Human Normal and Pathological Immune Responses. \emph{Frontiers in Immunology} 2018. doi: \httplink[10.3389/fimmu.2018.02679]{doi.org/10.3389/fimmu.2018.02679}
        \\ Pre-print: \emph{bioRxiv} 384172 (2018). doi: \httplink[10.1101/384172]{doi.org/10.1101/384172}.
        
        \item Semick SA, \textbf{Collado-Torres L}, Markunas CA, Shin JH, Deep-Soboslay A, Tao R, Huestis MA, Bierut LJ, Maher BS, Johnson EO, Hyde TM, Weinberger DR, Hancock DB, Kleinman JE$\dagger$, Jaffe AE$\dagger$. Developmental effects of maternal smoking during pregnancy on the human frontal cortex transcriptome. \emph{Molecular Psychiatry} 2018. doi: \httplink[110.1038/s41380-018-0223-1]{doi.org/10.1038/s41380-018-0223-1}
        \\ Pre-print: \emph{bioRxiv} 236968 (2017). doi: \httplink[10.1101/236968]{doi.org/10.1101/236968}.
        
        \item Jaffe AE, Straub R, Shin JH, Tao R, Gao Y, \textbf{Collado-Torres L}, Kam-Thong T, Xi HS, Quan J, Chen Q, Colantuoni C, Ulrich WS, Maher BJ, Deep-Soboslay A, The BrainSeq Consortium, Cross AJ, Brandon NJ, Leek JT, Hyde TM, Kleinman JE, Weinberger DR. Developmental and genetic regulation of the human cortex transcriptome illuminate schizophrenia pathogenesis. \emph{Nat. Neurosci.} 2018. doi: \httplink[10.1038/s41593-018-0197-y]{doi.org/10.1038/s41593-018-0197-y}.
        \\ Pre-print: \emph{bioRxiv} 124321 (2017). doi: \httplink[10.1101/145656]{doi.org/10.1101/124321}.
        
        \item Ellis SE, \textbf{Collado-Torres L}, Jaffe AE, Leek JT. Improving the value of public RNA-seq expression data by phenotype prediction. \emph{Nucl. Acids Res.} 2018. doi: \httplink[10.1093/nar/gky102]{doi.org/10.1093/nar/gky102}.
        \\ Pre-print: \emph{bioRxiv} 145656 (2017). doi: \httplink[10.1101/145656]{doi.org/10.1101/145656}.
        
        \item \textbf{Collado-Torres L}$\dagger$, Nellore A, Jaffe AE. 
        recount workflow: Accessing over 70,000 human RNA-seq samples with Bioconductor [version 1; referees: 1 approved, 2 approved with reservations]. \emph{F1000Research} (2017). doi: \httplink[10.12688/f1000research.12223.1]{doi.org/10.12688/f1000research.12223.1}.
        \\ Winning entry for the \httplink[Bioinformatics Peer Prize III]{bioinformatics-peer-prize-iii.thinkable.org}.
        
        \item Wright C, Shin JH, Rajpurohit A, Deep-Soboslay A, \textbf{Collado-Torres L}, Brandon NJ, Hyde TM, Kleinman JE, Jaffe AE, Cross AJ, Weinberger DR. Altered expression of histamine signaling genes in autism spectrum disorder. \emph{Translational Psychiatry} 2017. doi: \httplink[10.1038/tp.2017.87]{doi.org/10.1038/tp.2017.87}.
        
        \item \textbf{Collado-Torres L}$^{*}$, Nellore A$^{*}$, Kammers K, Ellis SE, Taub MA, Hansen KD, Jaffe AE, Langmead B, Leek JT. Reproducible RNA-seq analysis using \emph{recount2}. \emph{Nature Biotechnology} 2017. doi: \httplink[10.1038/nbt.3838]{doi.org/10.1038/nbt.3838}.
        \\ Pre-print: \emph{bioRxiv} 068478 (2016). doi: \httplink[10.1101/068478]{doi.org/10.1101/068478}.
        
        \item Nellore A, Jaffe AE, Fortin JP, Alquicira-Hernández J, \textbf{Collado-Torres L}, Wang S, Phillips RA, Karbhari N, Hansen KD, Langmead B, Leek JT. Human splicing diversity and the extent of unannotated splice junctions across human RNA-seq samples on the Sequence Read Archive. \emph{Genome Biology} 2016. doi: \httplink[10.1186/s13059-016-1118-6]{doi.org/10.1186/s13059-016-1118-6}.
        \\ Pre-print: \emph{bioRxiv} 038224 (2016). doi: \httplink[10.1101/038224]{doi.org/10.1101/038224}.
        
        \item \textbf{Collado-Torres L}, Nellore A, Frazee AC, Wilks C, Love MI, Langmead B, Irizarry RA, Leek JT, Jaffe AE. Flexible expressed region analysis for RNA-seq with derfinder. \emph{Nucl. Acids Res.} 2016. doi: \httplink[10.1093/nar/gkw852]{doi.org/10.1093/nar/gkw852}.
        \\ Pre-print: \emph{bioRxiv} 015370 (2016). doi: \httplink[10.1101/015370]{doi.org/10.1101/015370}.
        
        \item Nellore A, \textbf{Collado-Torres L}, Jaffe AE, Alquicira-Hernández J, Wilks C, Pritt J, Morton J, Leek JT, Langmead B. Rail-RNA: Scalable analysis of RNA-seq splicing and coverage. \emph{Bioinformatics} 2016. doi: \httplink[10.1093/bioinformatics/btw575]{doi.org/10.1093/bioinformatics/btw575}.
        \\ Pre-print: \emph{bioRxiv} 019067 (2015). doi: \httplink[10.1101/019067]{doi.org/10.1101/019067}.
        
        \item \textbf{Collado-Torres L}, Jaffe AE and Leek JT. regionReport: Interactive reports for region-level and feature-level genomic analyses [version2; referees: 2 approved, 1 approved with reservations]. \emph{F1000Research} 2016, 4:105. doi: \httplink[10.12688/f1000research.6379.2]{doi.org/10.12688/f1000research.6379.2}.
        \\ Pre-print: \emph{bioRxiv} 016659 (2015). doi: \httplink[10.1101/016659]{doi.org/10.1101/016659}.
        
        \item Jaffe AE, Shin J, \textbf{Collado-Torres L}, Leek JT, et al. Developmental regulation of human cortex transcription and its clinical relevance at single base resolution. \emph{Nat. Neurosci.} 2015. doi: \httplink[10.1038/nn.3898]{doi.org/10.1038/nn.3898}.
        
        \item Shank EA, Klepac-Ceraj V, \textbf{Collado-Torres L}, Powers GE, Losick R, Kolter R. Interspecies interactions that result in Bacillus subtilis forming biofilms are mediated mainly by members of its own genus. \emph{Proc. Natl. Acad. Sci.} U.S.A. 2011 Nov;108(48):E1236–1243. doi: \httplink[10.1073/pnas.1103630108]{doi.org/10.1073/pnas.1103630108}.
        
        \item Gama-Castro S, Salgado H, Peralta-Gil M, Santos-Zavaleta A, Muñiz-Rascado L, Solano-Lira H, Jimenez-Jacinto V, Weiss V, Garc\'ia-Sotelo JS, L\'opez-Fuentes A, Porr\'on-Sotelo L, Alquicira-Hern\'andez S, Medina-Rivera A, Mart\'inez-Flores I, Alquicira-Hern\'andez K, Mart\'inez-Adame R, Bonavides-Mart\'inez C, Miranda-R\'ios J, Huerta AM, Mendoza-Vargas A, \textbf{Collado-Torres L}, Taboada B, Vega-Alvarado L, Olvera M, Olvera L, Grande R, Morett E, Collado-Vides J. RegulonDB version 7.0: transcriptional regulation of Escherichia coli K-12 integrated within genetic sensory response units (Gensor Units). \emph{Nucleic Acids Res.} 2011 Jan;39(Database issue):D98–105. doi: \httplink[10.1093/nar/gkq1110]{doi.org/10.1093/nar/gkq1110}.
    \end{enumerate}
\subsection{Books}
    \begin{enumerate}
        \item Frazee AC, \textbf{Collado-Torres L}, Jaffe AE, Langmead B, Leek JT. Measurement, Summary, and Methodological Variation in RNA-sequencing in Statistical Analysis of Next Generation Sequencing Data, \emph{Springer}, 2014, 115-128.
    \end{enumerate}

