
\subsection{Bioconductor -- contributor role}
\cvitem{2019}{\httplink[brainflowprobes]{bioconductor.org/packages/brainflowprobes}}
\cvitem{2015}{\httplink[bumphunter]{bioconductor.org/packages/bumphunter}}
\cvitem{2014}{\httplink[ballgown]{bioconductor.org/packages/ballgown}}

\subsection{Other R packages}
\cvitem{2019}{\httplink[sgejobs]{github.com/LieberInstitute/sgejobs}: Helper functions for SGE jobs at JHPCE.}
\cvitem{2019}{\httplink[easyweb]{github.com/comunidadbioinfo/easyweb}: A fast and easy way to build your own website.}
\cvitem{2019}{\httplink[libdRSE]{github.com/LieberInstitute/libdRSE}: Custom RSE objects from genomic coordinates on LIBD data.}
\cvitem{2018}{\httplink[blogdown]{github.com/rstudio/blogdown}: contributor role, mainly in the \emph{Insert Image} and \emph{New Post} addins.}
\cvitem{2017}{\httplink[recount.bwtool]{github.com/LieberInstitute/recount.bwtool}: Compute coverage matrices from recount quickly using bwtool.}
\cvitem{2016-2019}{\httplink[jaffelab]{github.com/LieberInstitute/jaffelab}: commonly used functions by the Jaffe lab.}
\cvitem{2016}{\httplink[shinycsv]{github.com/LieberInstitute/shinycsv}: explore a table interactively.}
\cvitem{2014}{\httplink[enrichedRanges]{github.com/leekgroup/enrichedRanges}: identify enrichment between two sets of genomic ranges.}
\cvitem{2014}{\httplink[dots]{github.com/lcolladotor/dots}: simplify function calls.}
\cvitem{2013}{\httplink[fitbitR]{github.com/lcolladotor/fitbitR}: visualize your FitBit data.}
\cvitem{2011}{BacterialTranscription: identify TSSs and TUs from RNA-seq data.}

\subsection{shiny applications}
\cvitem{2019}{\httplink[recount-brain]{github.com/LieberInstitute/recount-brain}: explore recount-brain interactively at \httplink[jhubiostatistics.shinyapps.io]{jhubiostatistics.shinyapps.io/recount-brain/}.}
\cvitem{2018}{\httplink[wgbsExprs]{github.com/LieberInstitute/brain-epigenomics}: LIBD WGBS Expression explorer for the methylation and expression associations described by Price et al, 2019. \httplink[jhubiostatistics.shinyapps.io]{jhubiostatistics.shinyapps.io/wgbsExprs/}.}
\cvitem{2016}{\httplink[shinycsv]{github.com/LieberInstitute/shinycsv}: explore a table interactively deployed at \httplink[jhubiostatistics.shinyapps.io]{jhubiostatistics.shinyapps.io/shinycsv/}.}
\cvitem{2016}{\httplink[recount]{github.com/leekgroup/recount-website/tree/master/website}: analysis-ready RNA-seq gene and exon counts datasets deployed at \httplink[jhubiostatistics.shinyapps.io]{jhubiostatistics.shinyapps.io/recount/}.}
\cvitem{2014--2016}{MPH capstone TA \httplink[office hours sign up]{github.com/lcolladotor/MPHcapstoneTA}.}
\cvitem{2014}{\httplink[Simple mortgage calculator]{github.com/lcolladotor/mortgage}.}

\subsection{Miscellaneous}
\cvitem{2016}{Updated the JHU thesis template available via \httplink[GitHub]{github.com/lcolladotor/jhu-thesis-template} and \httplink[Overleaf]{www.overleaf.com/latex/templates/johns-hopkins-university-unofficial-thesis-template/tqdzgmrxgbtg}.}