\section{Teaching Experience}
\subsection{Instructor}

\begin{itemize}
\item PDCB-UNAM, Cuernavaca, MX

\cvitem{2011}{Invited instructor for the course \emph{Introduction to R and Biostatistics} \url{http://www.biostat.jhsph.edu/~lcollado/PDCB-Biostats.html} $\sim 10$ enrollment.} 
\cvitem{2010}{\emph{Analysis of High-Throughput Sequencing data with Bioconductor} for Biomedical Sciences PhD Program students \url{http://www.biostat.jhsph.edu/~lcollado/PDCB-HTS.html} $\sim10$ enrollment.}
 
\item CCG-UNAM, Cuernavaca, MX

\cvitem{2010}{\emph{Introduction to Using Bioconductor for High-Throughput Sequencing Analysis} practice lab at the \emph{National Bioinformatics Week} $\sim40$ enrollment.}

\item IBT-UNAM, Cuernavaca, MX

\cvitem{2010}{\emph{Introduction to R and plotting with R} course for Morett's lab $\sim10$ enrollment.}
\cvitem{2010}{Organized and gave a lecture for the course on \emph{Statistical Methods and Analysis of Genomic Data} \url{http://www.biostat.jhsph.edu/~lcollado/MEyAdDG.html} $\sim20$ enrollment.}
\cvitem{2009}{Organized the course \emph{Introduction to Bioinformatics} for Morett's lab and served as instructor for the \emph{Introduction to R and plotting with R} module \url{http://www.biostat.jhsph.edu/~lcollado/mIntroR.html} $\sim10$ enrollment.}

\item LCG-UNAM, Cuernavaca, MX

\cvitem{2009}{\emph{Seminar III: R/Bioconductor}. In-depth Bioconductor course \url{http://www.lcg.unam.mx/~lcollado/B/} $\sim30$ enrollment.}
\end{itemize}


\subsection{Guest lecturer}
\begin{itemize}
    
\item LCG-UNAM, Cuernavaca, MX

\cvitem{2012}{\emph{Introduction to R and Biostatistics} lecture for \emph{Seminar 1: Introduction to Bioinformatics} course $\sim30$ enrollment.}
\cvitem{2011}{\emph{Introduction to R and Biostatistics} lecture for \emph{Seminar 1: Introduction to Bioinformatics} course $\sim30$ enrollment.}
\end{itemize}


\subsection{Lead teaching assistant}
\begin{itemize}
    
\item JHSPH, Baltimore, US
    
\cvitem{2014--2015}{\emph{Statistical Methods in Public Health I} and \emph{II} $\sim550$ enrollment.}
\end{itemize}


\subsection{Teaching assistant}

\begin{itemize}
    
\item JHSPH, Baltimore, US

\cvitem{2015}{\emph{MPH capstone project}: 30 min one-on-one consulting sessions (biostatistics, Stata coding) $\sim500$ enrollment.}
\cvitem{2014}{\emph{MPH capstone project}: 30 min one-on-one consulting sessions (biostatistics, Stata coding) $\sim500$ enrollment.}
\cvitem{2013--2014}{\emph{Statistical Methods in Public Health I} and \emph{II} $\sim550$ enrollment.}
\cvitem{2012--2013}{\emph{Statistical Methods in Public Health I, II, III,} and \emph{IV} $\sim550$ enrollment.}

    
\item LCG-UNAM, Cuernavaca, MX

\cvitem{2009}{\emph{Principles of Statistics}. Basic R \url{http://www.lcg.unam.mx/~lcollado/E/} $\sim30$ enrollment.}
\cvitem{2008}{\emph{Bioinformatics and Statistics I}. R and Bioconductor overview \url{http://www.lcg.unam.mx/~lcollado/R/} $\sim40$ enrollment.}
\end{itemize}
