\section{Experience}
\subsection{Research}
\cventry{2016--current}{Staff Scientist II}{Andrew Jaffe lab}{LIBD, Baltimore, US}{}{At LIBD, Dr. Collado-Torres is part of the Data Science team which goals include better understanding and characterizing genomics signatures in the human brain, including DNA methylation and gene expression. Leonardo helps mentor other team members, provides support for LIBD projects and is advancing his academic career as part of Andrew Jaffe's lab. He is also a co-founder of the \httplink[LIBD rstats club]{LieberInstitute.github.io/rstatsclub/} and \httplink[CDSBMexico]{http://www.comunidadbioinfo.org/}.}
\cventry{2009--2011}{Bioinformatician}{Enrique Morett lab}{IBT-UNAM, Cuernavaca, MX}{}{Identified transcriptions start sites and transcription units in \emph{Escherichia coli} and \emph{Geobacter sulfurreducens} with RNA-seq data. Developed the \emph{BacterialTranscription} R package.}
\cventry{2007--2009}{Undergraduate research assistant}{Guillermo D\'avila lab}{CCG-UNAM, Cuernavaca, MX}{}{Determined bacteriophage ecological groups by developing a method based on codon distribution of all phage sequenced genomes. Joint work with Sur Herrera Paredes.}
\cventry{2007}{Undergraduate research assistant}{Roberto Kolter lab}{Harvard, Boston, US}{}{Supervisor: Elizabeth Shank. Carried out screenings to identify bacteria that activate the production of exopolysaccharide through the activation of the gene tasA in \emph{Bacillus subtilis}.}

\subsection{Industry}
\cventry{2009-2011}{Data Science Division Leader}{Winter Genomics}{Cuernavaca, MX}{}{Responsible for recruiting and hiring new personnel, overseeing and supervising bioinformaticians, training new employees, writing research reports and presenting them to colleagues, and organizing all scientific projects.\newline{}
\begin{itemize}
\item First scientific staff member at Winter Genomics;
\item Projects completed:
  \begin{itemize}
  \item de novo genome assembly simulations,
  \item assembly and annotation of the \emph{phiVC8} bacteriophage genome,
  \item integrated analysis of more than 20 RNA-seq samples for determination of transcription initiation in \emph{Escherichia coli} reported in Gama-Castro et al., \httplink[PMID 21051347]{www.ncbi.nlm.nih.gov/pubmed/21051347},
  \item de novo assembly of four \emph{Escherichia coli} strains and lead to Aguilar et al., \httplink[PMID 22884033]{www.ncbi.nlm.nih.gov/pubmed/22884033};
  \end{itemize}
\item Designed training material for new employees.
\end{itemize}}